---
title: "Lab 00 - Hello IDS!"
author: "Collin Megon"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Collin Megson", "Adi", "Niharika", 
           "Xu Sun", "Judy", "Cecilia"),
  github_username = c("CollinMegson", "adi-smh", "niharirajanala-bot", 
                      "emily-username", "Xiufeng992", "s2780666"), 
  colour = c("blue", "pink", "lavender", 
             "blue", "black", "yellow"),
  hobby = c("Tennis", "Theater", "Reading Books", 
            "Ice Hockey", "Video Games", "Sleeping"),
  favourite_number = c(2, 2, 7, 7, 3, 3)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


This plot shows the team members github Usernames and Favourite Numbers, along with filling the bars their favourite colour.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Username", 
          y = "Favourite Colour",
          title = "Team Colours")
```

I think labs renames the axis and title on the bar plot.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Perhaps just a list of peoples usernames and hobbies would be better.
